The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-11-11 paper/ms.tex
typos

\subsubsection{Chemical Compositions}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus. The chemical composition for the neutron capture elements were are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus. The elemental abundance rations were measured in order to asses the Galactic populations to which these stars belong. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\

@@

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[open orange squares,][]{Adibekyan2012}, \citet[light green circles][]{Battistini2015}. These elemental ratios give a representative example of the chemical composition of our sample and show they are consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}
One of the primary ways to distinguish, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, we can explore the ratio of their $\alpha$-elements to Fe. The $\alpha$ elements are formed during He burning (e.g. Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles) compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.}  to representative thick and thin disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.

For most of the stars in our sample, the [Mg/Fe] abundance ratios are enhanced. This is equally true in all of the $\alpha$-elements except Ca where the is a much larger spread.  The commonly used [$\alpha$/Fe] abundance ratio is the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4.0) ) is also enhanced in most stars. This is consistent with most of the stars observed here belonging to the Galactic disk with a slight (of the order $\sim$0.15~dex) enhancement in the $\alpha$-elements. Fig.~\ref{alphael} clearly rule out the Galactic bulge (which would require the sample to be significantly more $\alpha$-enriched given their metallicity) and the Galactic halo (given that the stars would need to be significantly more metal-poor). %Though there are a handful of stars where the typical [$\alpha$/Fe] ratio is solar.

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population. We do however observe that the Ba of our sample is slight enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}. However, we conclude in all elemental abundance ratios studied our sample most closely resembles the Galactic disk. 
\begin{figure*}
\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_ncap_pope.pdf}

>>>>

\subsubsection{Chemical Compositions}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus. The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus. The elemental abundance ratios were measured in order to assess the Galactic populations to which these stars belong. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\

@@

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[open orange squares,][]{Adibekyan2012}, \citet[light green circles][]{Battistini2015}. These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}
One of the primary ways to determine, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, is with the ratio of their $\alpha$-elements to Fe. The $\alpha$ elements are formed during He burning (e.g. Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles) compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.

For most of the stars in our sample, the [Mg/Fe] abundance ratios are enhanced. This is true for all of the $\alpha$-elements except Ca where the is a much larger spread. The commonly used [$\alpha$/Fe] abundance ratio, the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4) ), is also enhanced in most stars. This is consistent with most of the stars observed here belonging to the Galactic disk with a slight (of order $\sim$0.15~dex) enhancement in the $\alpha$-elements. Fig.~\ref{alphael} clearly rule out the Galactic bulge (which would require the sample to be significantly more $\alpha$-enriched given their metallicity) and the Galactic halo (given that the stars would need to be significantly more metal-poor). %Though there are a handful of stars where the typical [$\alpha$/Fe] ratio is solar.

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population. We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}. However, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk. 
\begin{figure*}
\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_ncap_pope.pdf}
